\input{standard-preamble.tex}

\begin{document}
\begin{adjustwidth}{}{-153pt}
\section{\bf Original Problem}

\begin{itemize}
	\item Restricted access to lab documents.
	\item Disorganized experiments documentation. Organized by course number only, with 8 character 		name.
	\item Experiments disappearing from memory. ie, crater lab, or projectile motion.
	\item Equipment stored in 16 different rooms.
	\item Equipment of unknown purpose taking up space.
\end{itemize}


\subsection{\bf Problems with former attempts}
\begin{itemize}
\item Heavy reliance on convention and standardization.
\end{itemize}


\section{\bf The Solutions}
\begin{itemize}
	\item Organized Lab Documents - Archive.
		\begin{itemize} \item {\bf Archive what students use, since that is what their comments 				will be 	based on.} \end{itemize}
	\item Department Wide Access to Information.
		\begin{itemize} \item {\bf IT working on adding to LDAP (similar to CAS) for controlled 				authentication.} \end{itemize}
	\item Transferable Knowledge.
		\begin{itemize} \item {\bf Place to hold all important information about a lab. Equipment, 			original papers, data, etc..} \end{itemize}
	\item Platform for Collaboration.
	\item Foundation for Future Development.
	\item Created Room to Grow.
		\begin{itemize} \item {\bf Remove what we don't need and create more physical space.}					\end{itemize}
	\item Tools for Ease of Upkeep.
		\begin{itemize} \item {\bf Tools for maintaining, manual for administrator.}\end{itemize}
	\item Mobile friendly.
\end{itemize}

\section{\bf Use Cases}

\subsection{\bf Instructor}
\begin{itemize}
\item What did the last instructor do?
\begin{itemize} \item {\bf 211 -> 2017 -> Fall}  \end{itemize}
\item What labs do we have for an Optics course?
\begin{itemize} \item {\bf clear filters -> Optics -> most recent}  \end{itemize}
\item What labs do we have on waves? 
\begin{itemize} \item {\bf clear filters -> Wave Mechanics -> most recent}  \end{itemize}
\item What math skills are required?
\begin{itemize} \item {\bf drop down menu on standing waves}  \end{itemize}
\end{itemize}

\subsection{\bf Lab Developer}
\begin{itemize}
\item I want to make changes to the current labs for my course?
\begin{itemize} \item {\bf 211 -> 2017 -> Fall -> ZIP}  \end{itemize}
\item Is there any background info on this lab?
\item Is there a template for a spreadsheet?
\item Do we have a lab on "Ampere's Law"?
\begin{itemize} \item {\bf clear filters -> search "Ampere"}  \end{itemize}
\item Time to build a brand new lab?
\begin{itemize} \item {\bf main page -> Instructor -> Lab LaTeX template}\end{itemize}
\item How where those diagrams made?
\begin{itemize} \item {\bf main page -> Instructor -> Tikz LaTeX example - view}\end{itemize}
\end{itemize}

\section{\bf Developing a new Experiment Slide}

\subsection{\bf Technical Staff}
\begin{itemize}
\item What equipment is needed for the lab?
	\begin{itemize} \item {\bf 211 -> 2017 -> Fall -> Static Equilibrium of a Balance Beam} \end{itemize}
\item How many labs is this equipment used in?
	\begin{itemize} \item {\bf 211 -> 2017 -> Fall -> Static Equilibrium of a Balance Beam} \end{itemize}
\item What is this item, and why do we needed it?
	\begin{itemize} \item {\bf inventory -> ST037 -> C3 -> Fluke Multimeter } \end{itemize}
\item What equipment needs attention?
	\begin{itemize} \item {\bf inventory -> 1-2 -> Fluke multimeter} \end{itemize}
\end{itemize}

\subsection{\bf Future Work}
\begin{itemize}
\item Continue to populate disciplines and topics
\item Authentication
\item Host Simulations
\item Demonstrations
\end{itemize}

\end{adjustwidth}
\end{document}